---
title: "Validating a brms model with targets"
author: "Andrew MacDonald"
format: html
---

```{r}
library(targets)
suppressPackageStartupMessages(library(tidyverse))
```


## Goal

to create a workflow for validating brms models using a targets pipeline

the idea is to use the tools already in brms and `targets` to automate this useful and common task.

* set up a model formula using `brms` syntax.
* define the priors using `brms` syntax
* simulate out of the prior using `brms`
* for each (of some sample of) prior simulation, fit the model using `targets` dynamic branching
* calculate the proportion of simulated datasets where the model was able to recover parameters
* put results in a markdown document with `tarchetypes::tar_quarto`

## Results

here is an example of some simulated datasets

```{r}
tar_load(prior_predictive_draws)

prior_predictive_draws |> 
  head() |> 
  unnest(simulated_data) |> 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = epred)) + 
  facet_wrap(~draw_id)
```

And here is the coverage for the different intervals:

```{r}
tar_load(coverage)

knitr::kable(coverage)
```


